Testing atlantisom: generate survey sampled length comps for Norwegian Barents Sea Atlantis

### 2019-05-20 TestSmallestLength.Rmd

Or do we need to change something about the length comp estimation?

>>>>

## Quick test with saved CCA census output

Here we check the CCA model (Atlantis Summit Common Scenario 1) saved length census output for small species at Isaac's suggestion:

```{r loadCCAlengthcomp, echo=TRUE}

source(here("config/CCConfig.R"))

length_censussurvsamp <- readRDS(file.path(d.name, paste0(scenario.name, "length_censussurvsamp.rds")))

Sardine:
```{r plotCCAsardine}
ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Pacific_sardine")

lfplot <- ggplot(ss_length_censussurvsamp, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, ss_length_censussurvsamp$species))

lfplot
```

Anchovy:
```{r plotCCAanchovy}
ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Anchovy")

lfplot <- ggplot(ss_length_censussurvsamp, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, ss_length_censussurvsamp$species))

lfplot
```

Herring:
```{r plotCCAherring}
ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Herring")

lfplot <- ggplot(ss_length_censussurvsamp, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name,ss_length_censussurvsamp$species))

lfplot
```

How do these three look?

Do we need to change something about the length comp estimation?

### 2019-05-20 visualization_Rmd/CCAStdSurvLengthCompTest.Rmd

atf_numsstd <- numsstd[numsstd$species == "Arrowtooth_flounder",]
atf_structnstd <- structnstd[structnstd$species == "Arrowtooth_flounder",]
atf_resnstd <- resnstd[resnstd$species == "Arrowtooth_flounder",]

atf_length_stdsurv <- calc_age2length(structn = atf_structnstd,
                                 resn = atf_resnstd,
                                 nums = atf_numsstd,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

lfplot <- ggplot(atf_length_stdsurv$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste(scenario.name, atf_length_stdsurv$natlength$species))

@@

# add sample, this is census, probably want it first?
lfplot <- ggplot(mapping=aes(x=upper.bins)) +
  geom_bar(data=lf_census_prop, aes(weight = atoutput/totlen), fill="blue") +
  geom_bar(data=lf_samp_prop, aes(weight = atoutput/totsamp), colour="red") +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste(scenario.name, lf_census_prop$species))

>>>>

ss_numsstd <- numsstd[numsstd$species == "Arrowtooth_flounder",]
ss_structnstd <- structnstd[structnstd$species == "Arrowtooth_flounder",]
ss_resnstd <- resnstd[resnstd$species == "Arrowtooth_flounder",]

ss_length_stdsurv <- calc_age2length(structn = ss_structnstd,
                                 resn = ss_resnstd,
                                 nums = ss_numsstd,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

lfplot <- ggplot(ss_length_stdsurv$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, ss_length_stdsurv$natlength$species))

@@

# add sample, this is census, probably want it first?
lfplot <- ggplot(mapping=aes(x=upper.bins)) +
  geom_bar(data=lf_census_prop, aes(weight = atoutput/totlen), fill="blue") +
  geom_bar(data=lf_samp_prop, aes(weight = atoutput/totsamp), colour="red") +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, lf_census_prop$species))

### 2019-05-20 visualization_Rmd/NOBAStdSurvLengthCompTest.Rmd
check gh lf in NOBA

@@

```{r allspplengthsamp, echo=TRUE}

>>>>

Sampling looks really different for greenland halibut than census did. Check this!

I'm using a shiny app for checking, which I'm not sure I want to launch from the html, so this code block is not evaluated. Can do interactively instead. It takes a few minutes to load the info:

```{r check-sampling, echo=TRUE, eval=FALSE}
# lets visualize which boxes we sampled and where greenland halibut are in NOBA
# use https://github.com/Atlantis-Ecosystem-Model/shinyrAtlantis
# I've already installed it, see readme for instructions
library(shinyrAtlantis)
obj <- make.sh.prm.object(file.path(d.name, box.file), 
                          file.path(d.name, functional.groups.file), 
                          file.path(d.name, biol.prm.file))
sh.prm(obj)

Our survey uses boxes 2:47 as parameterized here (somewhat randomly for testing). This is the NOBA map (copied from the shiny app):

```{r NOBAmap}
knitr::include_graphics("images/NOBAboxes.png")
```

Greenland halibut adults have a fairly high fraction in box 1, which we are missing with our survey, and we miss 48:57 where there are high (but not the highest) fraction of juveniles (screenshot of shiny app):

```{r GHRdist}
knitr::include_graphics("images/GRHdistNOBA.png")
```

Greenland halibut have 2 years per output age class. Our selectivity acts on the age class. We have them in the demersals group, so the selectivity curve is:

```{r sel-demersal}
plot(seldemersals$agecl, seldemersals$selex)
```

So we won't see any fish until they are almost 10, when they are pretty big, and we fully sample the larger fish. This combined with missing some juvenile areas may explain the strange shapes of the sampled length frequencies.

Here is the same survey missing the areas as described, but with full selectivity for all greenland halibut age classes:

```{r stdsurveyNbased-GHR, echo=TRUE}

ss.name <- funct.group.names[funct.group.names == "Green_halibut"]

selex1 <- data.frame(species=rep(funct.group.names, each=10),
                     agecl=rep(c(1:10),length(funct.group.names)),
                     selex=rep(1.0,length(funct.group.names)*10))

# get survey nums with full (no) selectivity
ss_survey_testNstd_nosel <- create_survey(dat = truth$nums,
                                 time = annualmidyear,
                                 species = ss.name,
                                 boxes = boxsurv,
                                 effic = efficmix,
                                 selex = selex1)

# now sample fish nums from this
ss_numsstd_nosel <- sample_fish(ss_survey_testNstd_nosel, effNmix)

# aggregate resn and struct n haven't changed because selectivity doesn't apply
# use the ones made above in the calc call with new nums

ss_length_stdsurv_nosel <- calc_age2length(structn = ss_structnstd,
                                 resn = ss_resnstd,
                                 nums = ss_numsstd_nosel,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

This should give the difference between missing key survey strata and survey selectivity, here set to capture all age classes perfectly:

```{r sslengthsamp2-test}

lfplot <- ggplot(ss_length_stdsurv_nosel$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, ss_length_stdsurv_nosel$natlength$species))

We may want to extend the length bins for something like greenland halibut, which get larger than the hardcoded largest bin in `calc_age2length`, 150 cm. Both census and these sampled length comps are chopped off at 150 cm for this species.

I will likely change the `calc_age2length` code to pass the upper bin of 150 as a default but allow the user to change it in the function call.

@@

```{r allspplengthsamp, echo=TRUE, eval=FALSE}
